%-*- program: xelatex -*-
%-*- program: biber -*-
%-*- program: xelatex -*-

\documentclass[11pt, a4paper]{article}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize} 
\subsubsectionfont{\mdseries\upshape\large} 

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm, 
bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
  pdftitle={tyler_reny_vita},
  pdfauthor={Tyler T. Reny},
  pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 

% DOCUMENT
\begin{document}
{\LARGE Tyler Reny}\\[1cm]
 University of California, Los Angeles\\
email: \href{mailto:ttreny@gmail.com}{ttreny@gmail.com}\\
website: \href{http://www.tylerreny.com}{tylerreny.com}\\ 
twitter: \href{http://www.twitter.com/tylerreny}{@tylerreny}\\ 
github: \href{https://github.com/tylerreny}{tylerreny}\\ 
google scholar: \href{https://scholar.google.com/citations?user=KTbztQUAAAAJ&hl=en}{Tyler Reny}\\ 

\section*{Current position}
\emph{PhD. Candidate}, UCLA Department of Political Science\\
Advisors: Matt Barreto (chair), Lynn Vavreck, David O. Sears, Efr$\acute{e}$n P$\acute{e}$rez, and Chad Hazlett

\section*{Education}
\years{2015}\textsc{MA} in Political Science, University of Washington, WA\\
\years{2011}\textsc{BA} in Government, Skidmore College, NY

\section*{Publications}

\href{https://dataverse.harvard.edu/dataverse/tylerreny}{[Replication Files]}\\

\subsection*{Journals}

\years{2019} 11. \textbf{Reny, Tyler}, Ali A. Valenzuela, and Loren Collingwood. 2019. ```No, You’re Playing the Race Card': Testing the Effects of Anti-Black, Anti-Latino and Anti-Immigration Appeals in the post-Obama Era''  \textit{Forthcoming at Political Psychology} \href{http://tylerreny.github.io/pdf/pubs/reny_etal_2019_polpsych.pdf}{[PDF]} \href{http://tylerreny.github.io/pdf/pubs/reny_etal_2019_polpsych_appendix.pdf}{[Appendix]} 
\begin{itemize}
  \item Press: \href{https://megaphone.link/VMP5167113125}{[Vox's The Weeds Podcast]} 
\end{itemize}

\years{} 10. \textbf{Reny, Tyler}, Loren Collingwood, and Ali Valenzuela. 2019. ``Vote Switching in the 2016 Election: Racial and Immigration Attitudes, Not Economics, Explains Shifts in White Voting''  \textit{Public Opinion Quarterly} 83(1): 91-113. \href{http://tylerreny.github.io/pdf/pubs/final_submission_reny_etal_poq_public.pdf}{[PDF]} \href{http://tylerreny.github.io/pdf/pubs/final_submission_reny_etal_poq_2018_appendix.pdf}{[Appendix]}

\begin{itemize}
  \item Press: \href{https://www.economist.com/united-states/2020/02/01/who-will-be-donald-trumps-most-forceful-foe}{[The Economist]} \href{https://www.economist.com/united-states/2019/07/04/the-best-line-in-the-first-televised-debate-may-hurt-the-democrats}{[The Economist]} \href{https://www.vox.com/policy-and-politics/2018/10/16/17980820/trump-obama-2016-race-racism-class-economy-2018-midterm}{[Vox.com]} \href{http://www.btrtoday.com/listen/thedailybeat/vote-switching-in-the-2016-election-with-tyler-reny-part-1/}{[Daily Beat Podcast Pt. 1]} \href{http://www.btrtoday.com/listen/thedailybeat/vote-switching-white-economic-anxiety-more-with-tyler-reny-part2/}{[Daily Beat Podcast Pt. 2]} \href{https://phys.org/news/2019-07-attitudes-immigration-underscored-vote-election.html}{[Phys.org]}
\end{itemize}

\years{2018} 9. \textbf{Reny, Tyler}, and Benjamin J. Newman. 2018. ``Protecting the Right to Discriminate: The Second Great Migration and Racial Threat in the American West.'' \textit{American Political Science Review.} 112(4): 1104-1110. \href{http://tylerreny.github.io/pdf/pubs/reny_newman_apsr_2018.pdf}{[PDF]} \href{http://tylerreny.github.io/pdf/pubs/reny_newman_apsr_2018_SI.pdf}{[Appendix]}
\begin{itemize}
  \item Awards: Charles Redd Award for Best Paper on Politics of the American West (WPSA 2018)
\end{itemize}

\years{} 8. Gest, Justin, \textbf{Tyler Reny}, and Jeremy Mayer. 2018. ``Roots of the Radical Right: Nostalgic Deprivation in the United States and Britain'' \textit{Comparative Political Studies} 51(13): 1694–1719. \href{http://tylerreny.github.io/pdf/pubs/reny_2017_cps_final.pdf}{[PDF]}\\

\years{} 7. \textbf{Reny, Tyler} and Paru Shah. 2018. ``Immigrant Political Ambition:  New Americans and the Quest for Political Office.'' \textit{Social Sciences Quarterly} 99(3): 1038-1059.\href{http://tylerreny.github.io/pdf/pubs/reny_shah_2018_ssq_immigrant_ambition.pdf}{[PDF]} 

\begin{itemize}
\item Press: \href{https://www.voanews.com/a/immigrants-candidates-make-a-run-for-it-in-upcoming-us-elections/4439132.html}{[Voice of America]}
\end{itemize}

\years{2017} 6. \textbf{Reny, Tyler}. 2017. ``Demographic Change, Latino Countermobilization, and the Politics of Immigration in U.S. Senate Campaigns'' \textit{Political Research Quarterly} 70(4): 735–748. \href{http://tylerreny.github.io/pdf/pubs/reny_2017_prq_final.pdf}{[PDF]} \href{http://tylerreny.github.io/pdf/pubs/reny_2017_prq_final_supp.pdf}{[Supplement]}\\

\years{} 5. Barreto, Matt, \textbf{Tyler Reny}, and Bryan Wilcox-Archuleta. 2017. ``Survey Methodology and the Latina/o Vote: Why a Bilingual, Bicultural, Latino-centered Approach Matters'' \textit{Aztl$\acute{a}$n: A Journal of Chicano Studies.} 42(2): 211-227.\href{http://tylerreny.github.io/pdf/pubs/reny_2017_aztlan_final.pdf}{ [PDF]}\\

\subsection*{Book Chapters and Other Publications}

\years{2019} 4. Valenzuela, Ali A. and \textbf{Tyler Reny}. 2019. ``Evolution of Experiments on Racial Priming''  \textit{Forthcoming in Advances in Experimental Political Science Eds. James N. Druckman and Donald P. Green} \href{http://tylerreny.github.io/pdf/pubs/ValenzuelaReny_racial_priming_cambridge_handbook.pdf}{[PDF]}\\

\years{} 3. \textbf{Reny, Tyler}, Bryan Wilcox-Archuleta, and Vanessa Cruz Nichols. 2019. ``Threat, Mobilization, and Latino Voting in the 2018 Election''  \textit{Forum: A Journal of Applied Research in Contemporary Politics} 16(4): 631–657 \href{http://tylerreny.github.io/pdf/pubs/reny_wilcox_cruz_nichols2019.pdf}{[PDF]} \\

\years{2017} 2. Garcia-Rios, Sergio I., Angela X. Ocampo, \textbf{Tyler Reny}, and Bryan Wilcox-Archuleta. 2017. ``El peso del voto latino en 2016.'' \textit{Foreign Affairs Latinoamerica} 17(1): 11-15. \href{http://tylerreny.github.io/pdf/pubs/reny_et_al_2017_foreign_affairs.pdf}{ [PDF]}\\

\years{2016} 1. \textbf{Reny, Tyler} and Sylvia Manzano. 2016. ``The Negative Effects of Mass Media Stereotypes of Latinos and Immigrants." In \textit{Media and Minorities: Questions on Representation from an International Perspective}. Eds Georg Ruhrmann, Yasemin Shooman, and Peter Widmann. Jewish Museum of Berlin Press. \href{http://tylerreny.github.io/pdf/pubs/reny_manzano_stereotypes_2016.pdf}{[PDF]}\\

\subsection*{Under review}

\years{} Reny, Tyler, and David O. Sears. ``Hands Off My Obamacare: Self-Interest and Symbolic Attitudes in The Health Care Debate''\\
%\years{} Reny, Tyler and Benjamin J. Newman. ``Racial Threat as Potential Outgroup Entry: Historical Evidence Using New Mass Transit''\\
%\years{} Newman, Benjamin J., Stephanie L. DeMora, and Tyler Reny. ``Female Empowerment and the Politics of Language: Evidence Using Gender-Neutral Amendments to State Constitutions''\\

\section*{Dissertation}

My dissertation explores group relations in geographic space and is guided by a central question: what happens when out-groups enter or attempt to enter homogeneous spaces dominated by a single group? How do these dominant groups respond to the perceived threat of “others”? In the first study which was published last year in the \textit{American Political Science Review}, I leverage a unique historical event, the migration of large numbers of black Southerners into California during the Second Great Migration (1940s-1960s), to estimate the effects of rapid demographic change on white voting. The second study investigates a previously unexplored vehicle for racial threat, new mass transit (NMT). NMT provides rapid and affordable arterial connections between segregated communities, potentially generating inter-group contact in communities that previously experienced very little. The study proposes that support for public goods can be shaped by this prospective group threat. I find evidence for this theory using voting data from a 1962 bond vote in San Francisco County that would provide funds for the Bay Area Rapid Transit (BART) system and facilitate the entry of black East Bay residents into primarily white inner-ring suburbs of San Francisco. The third project, which is scheduled for Fall 2019, plans to leverage an original lab experiment with UCLA students to examine how various types of intergroup contact---passive versus intensive, in-group versus out-group---shape attitudes about multiculturalism and behavior. 

\section*{Large Research Grants}

\years{2018}``How In-Group Elite Rhetoric Shapes Immigration Attitudes'' (Co-PI with Justin Gest) \textit{Partnership for a New American Economy} (\$73,375)\\

\section*{Small grants, fellowships, honors \& awards}

\years{2019}APSA Travel Grant (\$200)\\
\years{}Distinguished Junior Scholar Award from the APSA Political Psychology Section (\$400)\\
\years{2018}UCLA Fellowship in Political Psychology (\$500)\\
\years{}Charles Redd Award for Best Paper on Politics of the American West (WPSA 2018) (\$250)\\
\years{}APSA Political Communication Subsection Travel Award (\$700)\\
\years{}UCLA Hoffenberg Fellow\\
\years{}APSA Travel Grant (\$100)\\
\years{}CSREP Mark Q. Sawyer Professional Development Travel Grant (\$300)\\
\years{}Harrell Rodgers Graduate Student Travel Scholarship (\$500)\\
\years{}UCLA Fellowship in Political Psychology (\$500)\\
\years{2017}APSA First Generation Scholars in the Profession Travel Grant (\$250)\\
\years{}UCLA Luskin Center for History and Policy Fellowship (\$5,000)\\
\years{}UCLA Fellowship in Political Psychology (\$500)\\
\years{}UCLA Graduate Research Mentorship Award (\$36,000)\\
\years{}UCLA Graduate Research Summer Mentorship Award (\$6,000)\\
\years{2016}UCLA Hoffenberg Award\\
\years{}UCLA Fellowship in Political Psychology (\$500)\\
\years{}UCLA Graduate Research Mentorship Award (\$36,000)\\
\years{}UCLA Graduate Research Summer Mentorship Award (\$6,000)\\
\years{}APSA Warren E. Miller Fund Research Grant (\$2,000)\\
\years{2015} Department of Political Science Best Graduate Student Paper Award, University of Washington (\$500)\\
\years{2014} Donald R. Matthews Graduate Fellowship Summer Stipend, University of Washington (\$5,000)\\
\years{2013} Donald R. Matthews Graduate Fellowship, University of Washington (\$51,000)\\
\years{2011}\textit{Phi Beta Kappa}\\
Susan Riley Gunderson '64 Prize for Excellence in the Study of American Government (\$500)\\
\years{2009}\textit{Pi Sigma Alpha}\\
Levine Internship Award (\$3,000)\\

\subsection*{Informal \& reports}

\years{2019} ``Democracy Fund + UCLA
Nationscape Methodology and Representativeness Assessment'' with Chris Tausanovitch, Lynn Vavreck, Alex Rossell Hayes, and Aaron Rudkin (December). Nationscape. \href{https://www.voterstudygroup.org/download?lv=R9WVD6NcOZQVNZoKZOIRbASygr6H4fSnrLZ158RPvbx17XUGELPaq0KolDijyiTyN205aY805eFc2jdEul4iEsakXrQ50jcWVze58Hkn1FW6gSjR6OGY3IlQbtx6e%252BLQv0KjZJFudeXzYDWxzy6DuUdGxT2zwj0q8BzOOCMb3R%252Bx0Nz%252FlTNV9hE%252Fl8MgnTER0JU1SoCrk3o2mWygPDFDQBAEZixF4SmfssUk9Sl62Gd26KlJIInDvQ1j%252BAql0lUR}{[Link]}.\\
\years{2018} ``To win over moderates, Democrats need a coherent immigration policy'' with Justin Gest (July). LA Times Op-Ed. \href{http://www.latimes.com/opinion/op-ed/la-oe-gest-reny-immigration-policy-democrats-20180720-story.html}{[Link]}.\\
\years{} ``Should I Stay or Should I Go? How Effective Transit Oriented Development Can Lead to Positive Economic Growth Without Displacing Latinos'' (March). LPPI. \href{http://latino.ucla.edu/}{[Link]}.\\
\indent Press: 
\indent \href{https://www.mercurynews.com/2018/03/29/development-without-gentrification-oaklands-fruitvale-is-the-model-report-says/}{Mercury News} || 
\indent \href{https://www.citylab.com/equity/2018/04/how-transit-oriented-development-can-prevent-displacement/556373/?utm_source=twb%3Futm_source%3Dfbb}{Citylab} || \indent \href{https://blockclubchicago.org/2018/11/12/can-chicagos-gentrifying-neighborhoods-grow-without-leaving-longtime-residents-behind-oaklands-fruitvale-village-offers-hope/}{Block Club Chicago} ||
\indent \href{https://sf.curbed.com/2018/4/4/17198326/oakland-fruitvale-transit-village-housing-displacement-gentrification}{Curbed} || 
\indent \href{https://www.eastbayexpress.com/SevenDays/archives/2018/04/02/mondays-briefing-ucla-study-says-fruitvale-village-is-a-model-for-urban-planning-stephon-clark-protestor-struck-by-sacramento-sheriffs-veh}{East Bay Express}.\\
\years{} ``Why the GOP’s anti-immigration politics are here to stay.'' (July). LSE US Centre Blog. \href{http://blogs.lse.ac.uk/usappblog/2018/07/09/why-the-gops-anti-immigration-politics-are-here-to-stay/}{[Link]}.\\
\years{2017} ``In contrast to the exit poll, official election results in Illinois show Latino turnout was up and vote for Trump was down.'' (February). The Huffington Post. \href{http://huff.to/2lC9rc8}{[Link]}.\\
\years{} ``No, Trump didn't do surprisingly well among Latino voters: Let's once and for all dispense with that exit-poll-based fiction.'' (January). The New York Daily News. \href{http://nydn.us/2jtowIr}{[Link]}.\\
\years{2016} ``Trump fared worse than Romney in Florida Hispanic vote.'' (December). The Hill. \href{http://bit.ly/2gNFKOz}{[Link]}.\\
\years{2014}\textit{Minority Representation Gaps, by the Numbers} (October). Monkey Cage. The Washington Post. \href{http://wapo.st/ZGQntG}{[Link]}.\\
\years{}\textit{Represent 2020: Toward a Better Vision for Democracy} (September). New American Leaders Project. \href{http://bit.ly/1tLsVcV}{[Link]}.\\
\years{2013}\textit{Run Local: New American Electorate and the 2013 Municiple Elections} (March). New American Leaders Project. \href{http://bit.ly/WKwtGR}{[Link]}.\\
\years{}\textit{Obama Barely Touched Immigration in His Speech, but That's a Good Thing} (February). National Journal's Next America. \href{http://bit.ly/12R7lVG}{[Link]}.\\
\years{2012}\textit{From the Community to the Capitol: Immigrants Flex Political Muscle in the 2012 Congressional Races} (October). New American Leaders Project. \href{http://bit.ly/RLVzVF}{[Link]}.\\
\years{}\textit{How the U.S. is Still Struggling with Universal Suffrage} (September). National Journal's Next America.  \href{http://bit.ly/UDAUpD}{[Link]}.\\
\years{}\textit{Educating Tomorrow's Workforce is Crucial for America's Prosperity} (July). National Journal's Next America. \href{http://bit.ly/NCHoyf}{[Link]}.\\

\section*{Conference Presentations}

\years{}American Political Science Association Annual Conference (2016, 2017, 2018)\\
\years{}Western Political Science Association Annual Conference (2014, 2015, 2016, 2017, 2018, 2019)\\
\years{}Midwest Political Science Association Annual Conference (2015, 2017, 2018, 2019)\\
\years{}Politics of Race, Immigration, and Ethnicity Consortium Conference (PRIEC) (2014, 2015, 2016)\\
\years{}State Politics and Policy Conference (2013)

\section*{Additional Experience}
\years{2019-}Project Coordinator, Nationscape Survey\\
\years{2017-}Research Fellow, UCLA Latino Public Policy Institute (LPPI)\\
\years{2015-}Research Assistant, Assistant Professor Justin Gest, George Mason University\\
\years{2015-}Research Fellow, New American Leaders Project, NY\\
\years{2014-}Research Assistant, Professor Matt Barreto, UCLA\\
\years{2014}Research Consultant, New American Leaders Project, NY\\
\years{2011-2013}Program and Research Associate, New American Leaders Project, NY\\
\years{2011}Research Assistant for Associate Professor David Karp, Skidmore College, NY\\
\years{2011}Research Assistant for Dr. Tom Gais, Rockefeller Institute, NY\\
\years{2009-2011}Research Assistant for Professors Bob Turner and Patricia Ferraioli, Skidmore College, NY\\
\years{2011}Research Intern for Senator Olympia Snowe (ME), Washington, D.C.\\

\section*{Teaching}
\subsection*{Graduate Instructor}

\years{2016-2019} Graduate Bootcamp in R Statistical Programming\\
\years{2017-2019} Introduction to R\\
\years{2016-} Political Science Department R Maven\\

\subsection*{Undergraduate Instructor}

\years{2019} Instructor: 1960s Cluster: Data Analysis and Research Design\\
\years{2018} Instructor: Introduction to Data Analysis\\

\subsection*{Undergraduate TA}

\years{2018} TA: Political Communications. Professor Georgia Kernell.\\
\years{} TA: Political Communications. Professor Tim Groeling.\\
\years{2015} TA: Introduction to American Politics. Professor Mark Smith.\\
\years{} TA: Introduction to American Politics. Professor Megan Frances.\\
\years{2014} TA: Introduction to American Politics. Professor Becca Thorpe.

\section*{Service to the Discipline}

Reviewer for \textit{American Political Science Review, Journal of Politics, Political Behavior, Public Opinion Quarterly, Political Science Quarterly, Political Research Quarterly, American Politics Research, Translational Issues in Psychological Science}

\section*{Skills}

R, SPSS, STATA, Python, \LaTeX, SQLite, QGIS, GIMP\\
Webscraping\\
Proficient in Spanish\\
\\
\\
Updated January 2020

\end{document}