\documentclass[12pt]{article}

%\usepackage[citestyle=authoryear, natbib=true, url=false, doi=false, isbn=false, backend=bibtex]{biblatex}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage[margin=.5in]{geometry}
%WHEN YOU COMPILE YOU CAN CLEAN UP THE AUX FILES WITH COMMAND+L, DELETE
\begin{document}
\pagestyle{empty}
\noindent \textbf{{\LARGE POLS 202: Introduction to American Politics}}\\
\rule{\textwidth}{1pt}
\begin{flushright}\noindent Instructor: Professor Mark Smith\\
TA: Tyler Reny, PhD Student\\
Spring Quarter, 2015\\
University of Washington\\
\end{flushright}

\subsection*{Sections}
T/Th 8:30-9:20 | SAV 137\\
T/Th 9:30-10:20 | SMI 309

\subsection*{Contact Info}
Office: Smith 220B (next to computer lab)\\
Website: \url{www.tylerreny.com}\\
Email: \url{treny@uw.edu}

\subsection*{Availability and Email}

I will hold office hours on Wednesday from 9:30-11:30 or by appointment. I will hold longer blocks of office hours before exams to answer any questions you all may have. I strongly encourage you to come visit, chat about the college experience, clarify any confusion from lecture or section, or answer nagging questions you may have about this past season of Girls or Broad City. Unlike Yahoo Answers!, I may not have all the answers, but I'll do a better job than Kanye West on his new fashion line.

Email is to be used for class logistics only, not substantive questions. I will generally respond to emails within 24-48 hours of receiving them, except during weekends, on holidays, or during the 24 hours before an exam. As students at a Public Ivy institution, I expect that you will attend to important assignments with ample planning and foresight.

If I email the class, the email will be sent to your @uw.edu address. If you do not plan on checking this account regularly, please set up a forwarding service so that you don't miss any messages from me.

\subsection*{Expectations and Participation}

I expect that you will attend lecture, complete the assigned readings prior to our meetings, and show up on time each week. I will occasionally surprise you with mini-quizzes and short writing assignments in class. These will generally be quite easy and far less painful than Billy Dee Williams on \textit{Dancing with the Stars}.

Participation grades are partially based on attendance. If you are not in the room you cannot participate. If you miss section due to an illness, emergency, Taylor Swift matinee, or university-approved sporting event, please provide me with the relevant documentation (a doctor’s note, your student athlete travel schedule, or an envelope with 10 sequentially numbered \$100 bills). 

Anyone with disabilities, please register with the Disabilities Support Services Office and provide me with the necessary documentation as soon as possible. I will make every effort to be as accommodating as possible!

\subsection*{Plagiarism and Academic Honesty}

Plagiarism and cheating are violations of the UW student conduct code and will not be tolerated in this class. If you use another's work, regardless of the source (yes, Yahoo Answers counts), you must provide proper citations.  If plagiarism is suspected, your work will be presented to Professor Smith directly, and if necessary, university disciplinary channels will be invoked. If you are not sure what constitutes cheating, please consult: \url{http://depts.washington.edu/grading/conduct/} for more information. 

\subsection*{Grading}

Your final grade will be based on the rubric as outlined in Professor Smith's syllabus. 

\subsection*{Grading Appeals}

I will be responsible for grading all of your papers and exams in this course. I aim to be as fair as possible when assessing work produced in this class. All of the TAs share the same re-grade policy, which I list below:

\begin{enumerate}
 \item Carefully read all of the comments I have provided.
  \item Wait at least 24 hours and re-read the comments and your answers.
  \item Within \textit{one week} of receiving the grade, email me a one-page typed statement explaining specifically why the grade you received was not fair and needs to be altered.
  \item Come to my office hours (or by appointment), so that we can go over your work and talk about your appeal. If I believe your challenge is warranted I will re-grade it and return it to you during the next section we have together. 
  \item If you are dissatisfied with the re-grade, we can have another TA re-grade the exam a second time. Please note that this is your last option and that your grade may go up \textit{or down} with this final grading.
\end{enumerate}

\subsection*{Technology}
I realize that your cell phone is more precious to you than Kimmy Schmidt's smile. But I urge you to refrain from gratuitous texting during class. Plus, too much texting can cause you to think that Kim Kardashian's book of selfies is really worth the \$19.95. 

I allow laptops because I am not a complete luddite. I simply ask that you don't spend the entire class on distracting websites. You can check out that sweet text from Mom once section gets out. And that video of dogs trying to walk in shoes, while hilarious and well worth watching, can wait.

\end{document}